Playing multiple games using deep reinforcement learning

### 2019-09-10 multi_dqn_paper/paper.tex
some results
common

\documentclass[10pt,a4paper]{article}
\renewcommand{\baselinestretch}{1.0}
\usepackage{cite}
\usepackage[dvips]{graphicx}
\usepackage{psfrag}
\usepackage{color}
\usepackage[cmex10]{amsmath}
\usepackage{amsfonts}
\usepackage[font=footnotesize, captionskip=10pt]{subfig}
\usepackage{tikz}
\usepackage{flushend}
\usepackage{times}
\usepackage[margin=1.5cm]{geometry}
\usepackage[slovak]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

@@

Hyperparmaters of network were choosen as :
\begin{itemize}
    \item learning rate $\eta = 0.001$
    \item L1 and L2 regularization $\lambda _1 = \lambda _2 = 0.0000001$
    \item dropout $0.02$ (only after FC256 layer)
    \item minibatch size 32 for single DQN, 128 for multi DQN
\end{itemize}

@@

@@

@@

    \caption{Feature maps activity}\label{img:activity}
\end{figure}

>>>>

\documentclass[10pt,a4paper]{article}
\renewcommand{\baselinestretch}{1.0}
\usepackage{cite}
\usepackage[dvips]{graphicx}
\usepackage{psfrag}
\usepackage{color}
\usepackage[cmex10]{amsmath}
\usepackage{amsfonts}
\usepackage[font=footnotesize, captionskip=10pt]{subfig}
\usepackage{tikz}
\usepackage{flushend}
\usepackage{times}
\usepackage[margin=1.5cm]{geometry}
\usepackage[slovak, english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

@@

Hyperparmaters of network were choosen as :
\begin{itemize}
    \item learning rate $\eta = 0.001$
    \item L1 and L2 regularization $\lambda _1 = \lambda _2 = 0.0000001$
    \item dropout $0.02$ (only after FC256 layer)
    \item minibatch size 32 for single DQN, 128 for multi DQN
    \item gradient clip $\langle -10, 10 \rangle$
\end{itemize}

@@

First we presents training score progress. The games rewards has been chosen to
be impossible achieve positive score only by random playing. On figures \ref{img:score_result} we
can see typical RL training progress - first is agent playing randomly, taking negative rewards.
After few hundred games the agent finds good strategy and is able to achieve more and more positive
rewards.

As second part, we focused on learned features visualisation. We processed the maximum kernel response, for
all networks and all kernels. The inputs for maximum kernel response are presented on figure \ref{img:max_response}.
Those images are obtained by maximizing kernel response using gradient backpropagation, starting with random input (cite). We
visualised only convolutional layers.

To compare trained networks for learning similar features we computed correlations between networks (TODO more specify how).
Considering networks features correlation (Table \ref{tab:networks_correlation}) we assume that
multi\_net\_0 is learning different features. But we can see strongest correlation with most complicated games - Pacman and Snake,
and the lowest correlation with the simplest game - Pong \footnote{most/less complicated game - in meaning of input complexity}.

This results leads us to visualise activation heatmap - to understand what are different networks focusing on.

@@

\begin{figure}[htb!]
\centering
\includegraphics[width=0.7\textwidth]{results/activity/kernel_features_desc.png}
\caption{Kernel maximum response inputs visualisation for different networks}\label{img:max_response}
\end{figure}

\iffalse

@@

    \caption{Feature maps activity}\label{img:activity}
\end{figure}
\fi

\begin{table}[htb!]
\begin{tabular}{|l|c|c|c|c|c|c|c|l|}
\hline
\textbf{network}       & \textbf{arkanoid} & \textbf{enduro} & \textbf{invaders} & \textbf{pacman} & \textbf{pong} & \textbf{snake} & \textbf{multi\_net\_0} & \textbf{summary} \\ \hline
\textbf{arkanoid}      & 1.0               & 0.152           & 0.184             & 0.177           & 0.14          & 0.172          & 0.171                  & \textbf{1.9951}  \\ \hline
\textbf{enduro}        & 0.18              & 1.0             & 0.241             & 0.252           & 0.103         & 0.169          & 0.186                  & \textbf{2.1308}  \\ \hline
\textbf{invaders}      & 0.189             & 0.205           & 1.0               & 0.203           & 0.112         & 0.164          & 0.16                   & \textbf{2.0330}  \\ \hline
\textbf{pacman}        & 0.194             & 0.232           & 0.243             & 1.0             & 0.14          & 0.17           & 0.227                  & \textbf{2.2048}  \\ \hline
\textbf{pong}          & 0.118             & 0.076           & 0.086             & 0.116           & 1.0           & 0.092          & 0.114                  & \textbf{1.6013}  \\ \hline
\textbf{snake}         & 0.223             & 0.239           & 0.208             & 0.222           & 0.154         & 1.0            & 0.268                  & \textbf{2.3137}  \\ \hline
\textbf{multi\_net\_0} & 0.166             & 0.171           & 0.155             & 0.207           & 0.127         & 0.202          & 1.0                    & \textbf{2.0283}  \\ \hline
\end{tabular}

\caption{Networks correlation}\label{tab:networks_correlation}

\end{table}
